Evolutionary market ecologies and market malfunction\\ Draft

### 2021-07-06 draft.tex
Updates from Overleaf

\subsection{Market ecology and malfunction/dynamcs}
\subsection{Learning in financial markets}
\subsection{Research questions and motivation}
\subsection{Model}
\subsection{Main results and implications}

\boldred{Introduction TBD}
\boldred{Everything related to GP and multi asset: in footnotes}
% Maybe paragraphs could be
% market ecology
% evolutionary computation
% evolution in financial markets

>>>>

\subsection{Market ecology and malfunction/dynamics}
\boldred{related work and gap that we fill}
\subsection{Learning in financial markets}
\boldred{related work and gap that we fill}
\subsection{Research questions and motivation}
\subsection{Model}
\subsection{Main results and implications}
What he hope to show:
\begin{itemize}
    \item Taking learning into account changes the stability regions of the model (regions of the strategy space that we thought to be stable/unstable are actually different)
    \item Taking learning into accounts allows to get more realistic in terms of stylized facts
    \item Learning shows more complex behaviors, cycles and complexity
    \item \boldred{policy implications}
\end{itemize}

\boldred{Introduction TBD}
\boldred{Everything related to GP and multi asset: in footnotes}
\boldred{a literature review}
% Maybe paragraphs could be
% market ecology
% evolutionary computation
% evolution in financial markets
